Bayesian methods for black hole merger parameter estimation with LISA.

### 2018-11-20 paper/paper_PE.tex
Paper : reorganized sections
Paper : pushed TODOs for plots in README and changed section structure.
Paper : small edit.

@@

@@

\section{Methodology}
\label{sec:intro}

\subsection{Fast frequency domain LISA response}
\label{sec:response}

\subsection{Fast likelihood computation}
\label{sec:likelihood}

@@

\subsection{Temporal development of SNR}
\label{sec:timeSNR}

\subsection{LISAframe parameters}
\label{sec:LISAframe}

@@

In each channel, we separate the contribution of the modes $h_{22}$ and $h_{2,-2}$ as
\bsub\label{eq:defsase}
\begin{align}
	s_{a} &= a_{22} + a_{2,-2} \,, \\
	s_{e} &= e_{22} + e_{2,-2} \,,
\end{align}
\esub
with
\bsub\label{eq:defa22a2m2}
\begin{align}
	a_{22} &= \frac{3i}{4d} \sqrt{\frac{5}{\pi}} \cos^{4}\frac{\iota}{2} e^{2i(-\varphiL-\psiL)} \left( D_{a}^{+} + i D_{a}^{\times} \right) \,, \\
	a_{2,-2} &= \frac{3i}{4d} \sqrt{\frac{5}{\pi}} \sin^{4}\frac{\iota}{2} e^{2i(-\varphiL+\psiL)} \left( D_{a}^{+} - i D_{a}^{\times} \right) \,.
\end{align}
\esub
and similarly for the E channel with~\eqref{eq:defDe} instead of~\eqref{eq:defDa}
\bsub\label{eq:defe22e2m2}
\begin{align}
	e_{22} &= \frac{3i}{4d} \sqrt{\frac{5}{\pi}} \cos^{4}\frac{\iota}{2} e^{2i(-\varphiL-\psiL)} \left( D_{e}^{+} + i D_{e}^{\times} \right) \,, \\
	e_{2,-2} &= \frac{3i}{4d} \sqrt{\frac{5}{\pi}} \sin^{4}\frac{\iota}{2} e^{2i(-\varphiL+\psiL)} \left( D_{e}^{+} - i D_{e}^{\times} \right) \,.
\end{align}
\esub
Here, we introduced the dimensionless luminosity distance ratio $d \equiv D / D^{\rm inj}$.

@@

The conditions~\eqref{eq:defr}-\eqref{eq:rcondition} can be inverted for the sky position as follows. For a given complex value of $r$, $r(\lambda_{L}^{*}, \beta_{L}^{*}) = r$ can be rewritten as
\be\label{eq:eqtosolveforlambdabetaL}
	e^{4i\lambda_{L}^{*}}e^{i\frac{\pi}{3}} \frac{\left( 1 +\sin\beta_{L}^{*} \right)^{2}}{\left( 1 - \sin\beta_{L}^{*} \right)^{2}} = \frac{1+ i r}{1 - i r} \,.
\ee
Solving for the modulus of~\eqref{eq:eqtosolveforlambdabetaL} then yields
\be\label{eq:solutionbetaL}
	\sin\beta_{L}^{*} = \frac{\rho - 1}{\rho + 1} \,,
\ee
for
\be
	\rho = \sqrt{\left| \frac{1+ i r}{1 - i r} \right|} \,.
\ee
Solving for the argument of~\eqref{eqtosolveforlambdabetaL} gives four solutions for $\lambda_{L}^{*}$ as
\be\label{eq:solutionlambdaL}
	\lambda_{L}^{*} = - \frac{\pi}{12} + \frac{1}{4}\mathrm{Arg} \frac{1+ i r}{1 - i r} + \frac{k \pi}{2} \quad \mathrm{for} \quad k = 0,\dots,3 \,.
\ee

@@

\section{Illustrating examples}
\label{sec:examples}

@@

\subsection{A non-degenerate case}
\label{sec:high-M-non-deg}

@@

\subsection{Stellar origin black holes}
\label{sec:SOBH}

\subsection{Highlighting degeneracies}
\label{sec:degen}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Instrument response}
\label{sec:response}

@@

\subsection{The LISA response}
\label{sec:lisaresponse}

@@

\subsection{LISA-frame parameters}
\label{sec:LISAframe}

@@

In each channel, we separate the contribution of the modes $h_{22}$ and $h_{2,-2}$ as
\bsub\label{eq:defsase}
\begin{align}
	s_{a} &= a_{22} + a_{2,-2} \,, \\
	s_{e} &= e_{22} + e_{2,-2} \,,
\end{align}
\esub
with
\bsub\label{eq:defa22a2m2}
\begin{align}
	a_{22} &= \frac{3i}{4d} \sqrt{\frac{5}{\pi}} \cos^{4}\frac{\iota}{2} e^{2i(-\varphiL-\psiL)} \left( D_{a}^{+} + i D_{a}^{\times} \right) \,, \\
	a_{2,-2} &= \frac{3i}{4d} \sqrt{\frac{5}{\pi}} \sin^{4}\frac{\iota}{2} e^{2i(-\varphiL+\psiL)} \left( D_{a}^{+} - i D_{a}^{\times} \right) \,.
\end{align}
\esub
and similarly for the E channel with $D_{e}^{+,\times}$ instead of $D_{a}^{+, \times}$ as
\bsub\label{eq:defe22e2m2}
\begin{align}
	e_{22} &= \frac{3i}{4d} \sqrt{\frac{5}{\pi}} \cos^{4}\frac{\iota}{2} e^{2i(-\varphiL-\psiL)} \left( D_{e}^{+} + i D_{e}^{\times} \right) \,, \\
	e_{2,-2} &= \frac{3i}{4d} \sqrt{\frac{5}{\pi}} \sin^{4}\frac{\iota}{2} e^{2i(-\varphiL+\psiL)} \left( D_{e}^{+} - i D_{e}^{\times} \right) \,.
\end{align}
\esub
Here, we introduced the dimensionless luminosity distance ratio $d \equiv D / D^{\rm inj}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Methodology}
\label{sec:method}

@@

\subsection{Frequency domain LISA response}
\label{sec:response}

\subsection{Likelihood computation}
\label{sec:likelihood}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Signals and transfer functions}
\label{sec:signaltransfer}

\subsection{Time and frequency accumulation of SNR}
\label{sec:timefreqSNR}

\section{Supermassive black holes}
\label{sec:SMBH}

@@

\subsection{A non-degenerate case}
\label{sec:SMBHPEnondeg}

@@

\subsection{Accumulating signal with time}
\label{sec:SMBHPEacctime}

\subsection{SNR dependence of parameter estimation}
\label{sec:SMBHPEdistance}

\subsection{Highlighting degeneracies}
\label{sec:SMBHPEdegen}

@@

The conditions~\eqref{eq:defr}-\eqref{eq:rcondition} can be inverted for the sky position as follows. For a given complex value of $r = s_{a}^{\rm inj} / s_{e}^{\rm inj}$, $r(\lambda_{L}^{*}, \beta_{L}^{*}) = r$ can be rewritten as
\be\label{eq:eqtosolveforlambdabetaL}
	e^{4i\lambda_{L}^{*}}e^{i\frac{\pi}{3}} \frac{\left( 1 +\sin\beta_{L}^{*} \right)^{2}}{\left( 1 - \sin\beta_{L}^{*} \right)^{2}} = \frac{1+ i r}{1 - i r} \,.
\ee
Solving for the modulus of~\eqref{eq:eqtosolveforlambdabetaL} then yields
\be\label{eq:solutionbetaL}
	\sin\beta_{L}^{*} = \frac{\rho - 1}{\rho + 1} \,,
\ee
for
\be
	\rho = \sqrt{\left| \frac{1+ i r}{1 - i r} \right|} \,.
\ee
Solving for the argument of~\eqref{eq:eqtosolveforlambdabetaL} gives four solutions for $\lambda_{L}^{*}$ as
\be\label{eq:solutionlambdaL}
	\lambda_{L}^{*} = - \frac{\pi}{12} + \frac{1}{4}\mathrm{Arg} \frac{1+ i r}{1 - i r} + \frac{k \pi}{2} \quad \mathrm{for} \quad k = 0,\dots,3 \,.
\ee

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Stellar origin black holes}
\label{sec:SOBH}
